\chapter{Introduction}

\label{chap:Intro}

Diamond: An Online Tool for Card Sorting and Tree Testing was created as an 
extension of the TreeTest tool, which was implemented by Ajdin Mehic as part 
of his Master's Thesis~\parencite{TreeTest}. 
Because of providing both 
functionalities a card sorting tool and a tree testing tool now the application 
was combined under the new name.

In this report you will find a brief introduction to card sorting and an explanation 
of all technologies used to create Diamond. The implementation steps are also 
listed and explained in a constructive manner. Finally, there are expansion 
ideas for the future and final remarks mentioned.


\section{Creating a Card-Sorting Application}

Since there are already many tools out there, it is not easy to find a good 
approach to implement a new app in this sector. One of the best existing 
examples is OptimalSort~\parencite{OptimalSort}.

At Diamond the main target was to keep it simple, but also to equip it with
many features as possible. Therefore, the card sorting process itself is 
designed very intuitive, but also the setup process of a new study is created 
clean and straightforward. Here it is possible to create cards rapidly via 
.csv import.

In addition to editing and deleting, the status of each single study can be 
determined. For this you can switch between launch and unlaunch. For
launched studies you can easily send an invitation link to the users.

Finally, after completition of all the participants, you also have the opportunity 
to export the results as .csv in different ways.

