\chapter{Concluding Remarks}

\label{chap:Concl}



\section{Tool Comparison}

Because the tested tools differ due to their features and are also designed for
different tasks, the average value of all the evaluation ratings was calculated. 

Finally, a brief summary of the results and ratings including all reviewed tools 
can be seen in Table~\ref{tab:tool-comparison}.




\begin{table}[tpb]
\centering
\begin{tabularx}
{\linewidth}{|X|c|c|c|c|c|}
\hline \textbf{Name} & \textbf{Simplicity} & \textbf{Documentation} & \textbf{Features} & \textbf{Business Model} & \textbf{Average}\\ 
\hline OptimalSort & 4 & 5 & 5 & 3 & 4.25 \\ 
\hline UXtweak & 5 & 4 & 4 & 3 & 4.00 \\ 
\hline ProvenByUsers & 4 & 4 & 4 & 1 & 3.50 \\ 
\hline Casolysis & 4 & 0 & 4 & 5 & 3.25 \\ 
\hline kardSort & 5 & 1 & 1 & 5 & 3.00 \\ 
\hline SynCaps v3 & 1 & 2 & 4 & 5 & 3.00 \\ 
\hline xSort & 2 & 2 & 3 & 4 & 2.75 \\ 
\hline CSA & 0 & 0 & 4 & 0 & 1.00 \\ 
\hline
\end{tabularx} 
\caption[Tool Comparison] 
{ 
This table summarizes all the ratings from the reviewers, sorted by the computed average value.
}
\label{tab:tool-comparison}
\end{table}




\section{Recommendations}

With reference to the overview of all the reviewed tools which can be seen 
in Table~\ref{tab:tool-comparison}, it is recommended to make three 
categories of recommendations: One for the best allrounder, another one 
for the best bang of your buck and a third one for the offline card sorting.

OptimalSort has emerged as the best allrounder, even if you only find a 
limited number of participants and cards to use in the free version. But 
the pretty good usability and all the analysis tools speak for themselves.

As the best bang for your buck the fully free card sorting tool kardSort 
in combination with a free analysis tool, e.g., Casolysis or SynCaps, would
be the best choice. Carrying out the study with kardSort is very intuitive and 
easy to handle. Furthermore, all the sorting data can be easily exported 
to SynCaps, where you can analyze it afterwards.

For offline card sorting the good old paper cards are definitely the easiest
and best way to use. In combination with an analysis in SynCaps this
method can keep up with many online tools.

